Consider a case in which the option seller, only has one kind of asset and wants to sell options in different kind of assets (different kind of coins). He can do the change in two different manners: 1- make a chain of swaptions 2- put a ratio to handle currency fluctuations and at the time of exercising the option, put the ratio into an auction to convert it to needed currency (Bcoin).

The second scenario seems rational if the option seller is a big deep market of cryptocurrencies and can afford to put principals more than the equivalent counter party's principal, but in another cryptocurrency.
As an instance, imagine Bob is the option seller and all his asset is in Bcoins. Alice is the option buyer and her asset is in Acoins which she wants to swap with some Ccoins. Bob enters a swaption with Alice which exchanges Acoins with Bcoins. This is not what Alice really wanted (she needed Ccoins), so Bob should put more Bcoins in order to handle future changes in value of assets. At the time of exercising the option, Bob's money will be sent to a atomic swap with a very short duration and a secret that is owned by Bob. Because of the short locktimes, the premium needed in atomic swap is negligible. The counter party of the atomic swap also is Bob and he is given this short opportunity to change the Bcoins, with the amount of Ccoins Alice had requested. If Bob fails to provide Alice with needed Ccoins, Alice would swap Bcoins with her needed asset in other swaptions or atomic swaps. As Bcoins where over-collateralized, this would be easy for Alice to do so.